DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-09-27 paper/intro.tex
restructure

%
%  $Author: ienne $
%  $Date: 1995/09/15 15:20:59 $
%  $Revision: 1.4 $
%

% \documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}   %%%tc version
\documentclass[10pt, conference]{IEEEtran}
%\documentclass[conference,compsoc]{IEEEtran}
%\documentclass[10pt, conference]{IEEEtran}
%\documentclass[times, 10pt,onecolumn]{article}
\usepackage{amsmath, amssymb, enumerate}

%%%%%%%%%%%%%%%% page control%%%%%%%%%%%%%%%%%
%\usepackage[margin=0.75in]{geometry}

%\linespread{0.991}  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% this is really useful
%\usepackage{cite}
\usepackage{fancybox}
\usepackage{amsfonts}
%\usepackage{algorithm}
%\usepackage[noend]{algorithmic}
\usepackage[usenames]{color}
%\usepackage{colortbl}
%\usepackage[ figure, boxed, vlined]{algorithm2e}
%\usepackage[linesnumbered,vlined]{algorithm2e}
%\usepackage[lined,boxed]{algorithm2e}
\usepackage{listings}

\usepackage[linesnumbered,vlined]{algorithm2e}
\usepackage{graphicx}
\usepackage{times}
\usepackage{psfrag}
\usepackage{subfigure}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{multirow}
%\usepackage{setspace}
%\usepackage{listings}
\usepackage{epsfig}
%\usepackage{epstopdf}
%\usepackage[font=small,labelfont=bf]{caption}
\usepackage{url}

\usepackage{color}
\def\fixme#1{\typeout{FIXED in page \thepage : {#1}}
%\bgroup \color{red}{} \egroup}
\bgroup \color{red}{[FIXME: {#1}]} \egroup}

%\usepackage[pdftex]{hyperref}
\usepackage{rotating,tabularx}

\interfootnotelinepenalty=10000

%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother

%\documentstyle[times,art10,twocolumn,latex8]{article}

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
\pagestyle{plain}
%\thispagestyle{empty}
%\pagestyle{empty}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

%% remaining budget share, used in task stall section.
\newcommand{\bottomrule}{\hline}
\newcommand{\toprule}{\hline}
\newcommand{\midrule}{\hline}
%-------------------------------------------------------------------------
\begin{document}

\title{DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car}
\author{Author One, Author Two\\
\{author1,author2\}@ku.edu\\
University of Kansas, USA\\ 
}

\maketitle
\thispagestyle{empty}
\begin{abstract}

Abstract goes here.

\end{abstract}

%-------------------------------------------------------------------------

%% UPenn's f1/10 BOM: $3,628.37	
%% http://f1tenth.org/
%% http://selfdrivingcars.mit.edu/
%% http://fast.scripts.mit.edu/racecar/
%% https://github.com/mit-racecar

\section{Introduction}
Autonomous vehicles have been a topic of increasing interest in many
disciplines in recent years. Due to the nature of autonomous vehicles,
it is necessary that all real-time operations are successfully
performed prior to their deadlines. This requires that the AV platform
be capable of completing all necessary computations in a timely
manner, while maintaining a high level of accuracy. Consequently, the
cost of creating a platform capable of self-driving can be relatively
high, especially in the current cost-sensitive climate of the
automotive industry \cite{}. The overall price for an autonomous
vehicle platform currently acts as a bottleneck, especially from an
academic standpoint, where cost is an important factor. For many
researchers and students, the charge associated with autonomous
vehicle research is a significant barrier. These same parties may also
be deterred from participating in autonomous vehicle research due to
the potential for their developed platforms to break in the
experimental process. The idea of building one relatively expensive
platform may not be too daunting for some, but the notion of
potentially making multiple identical platforms in case of accidents
may be overwhelming. Toward this end, we explore the possibility of
developing a low-cost system that still employs state-of-the-art AI
technologies and is capable of executing real-time autonomous vehicle
operations.

@@

The primary {\bf contributions} of this paper are as follows:
\begin{itemize}
  \item We present the design, implementation, and case-study of a low-cost
    autonomous vehicle that utilizes the state-of-the-art aritificial 
    intelligence techniques.
  \item We systematically analyze real-time characteristics of
    multiple embedded computing platform, including the Raspberry Pi 3
    Model B, in the contex of a vision-based autnomous driving.
\end{itemize}

@@

\section{Background}
Cite a paper \cite{barroso2009datacenter}.

Cite multiple papers \cite{banga99resourcecontainers,barroso2009datacenter}

\section{Platform Overview}
...
\section{Data Collection}
...
\section{Network Architecture}
...
\section{Real-Time DNN Inferencing}
...
\section{Online/Offline Training}
...
\section{Evaluation}
...
\section{Related Work}
\cite{Bojarski2016}

\section{Conclusion}
%-------------------------------------------------------------------------

\bibliographystyle{plain}
\bibliography{reference}
\end{document}

>>>>

\section{Introduction} \label{sec:intro}

Autonomous vehicles have been a topic of increasing interest in many
disciplines in recent years. Due to the nature of autonomous vehicles,
it is necessary that all real-time operations are successfully
performed prior to their deadlines. This requires that the AV platform
be capable of completing all necessary computations in a timely
manner, while maintaining a high level of accuracy. Consequently, the
cost of creating a platform capable of self-driving can be relatively
high, especially in the current cost-sensitive climate of the
automotive industry \cite{}. The overall price for an autonomous
vehicle platform currently acts as a bottleneck, especially from an
academic standpoint, where cost is an important factor. For many
researchers and students, the charge associated with autonomous
vehicle research is a significant barrier. These same parties may also
be deterred from participating in autonomous vehicle research due to
the potential for their developed platforms to break in the
experimental process. The idea of building one relatively expensive
platform may not be too daunting for some, but the notion of
potentially making multiple identical platforms in case of accidents
may be overwhelming. Toward this end, we explore the possibility of
developing a low-cost system that still employs state-of-the-art AI
technologies and is capable of executing real-time autonomous vehicle
operations.

@@

The {\bf contributions} of this paper are as follows:
\begin{itemize}
  \item We present the design and implementation of a
    low-cost autonomous vehicle testbed DeepPicar, which utilizes the
    state-of-the-art aritificial intelligence techniques.
  \item We provide an analysis and case-study of real-time issues in the
    DeepPicar.
  \item We systematically compare real-time computing capabilities of
    multiple embedded computing platforms in the contex of a
    vision-based autnomous driving.
\end{itemize}

@@

### 2017-09-27 paper/main.tex
restructure

\section{Introduction}
Autonomous vehicles have been a topic of increasing interest in many
disciplines in recent years. Due to the nature of autonomous vehicles,
it is necessary that all real-time operations are successfully
performed prior to their deadlines. This requires that the AV platform
be capable of completing all necessary computations in a timely
manner, while maintaining a high level of accuracy. Consequently, the
cost of creating a platform capable of self-driving can be relatively
high, especially in the current cost-sensitive climate of the
automotive industry \cite{}. The overall price for an autonomous
vehicle platform currently acts as a bottleneck, especially from an
academic standpoint, where cost is an important factor. For many
researchers and students, the charge associated with autonomous
vehicle research is a significant barrier. These same parties may also
be deterred from participating in autonomous vehicle research due to
the potential for their developed platforms to break in the
experimental process. The idea of building one relatively expensive
platform may not be too daunting for some, but the notion of
potentially making multiple identical platforms in case of accidents
may be overwhelming. Toward this end, we explore the possibility of
developing a low-cost system that still employs state-of-the-art AI
technologies and is capable of executing real-time autonomous vehicle
operations.

In this paper, we present DeepPicar, or Picar for short, a low-cost
autonomous car platform that can be utilized in research and
education. We follow the same methodology found in other platforms,
such as NVIDIA’s end-to-end vision based control \cite{}, but
implement it on a smaller scale. The Picar is comprised of a Raspberry
Pi 3 Model B, a camera and a low cost RC car. By creating and using
the Picar platform, we seek to accomplish the following three
goals. First, the significant reduction of the overall cost required
would make autonomous driving research more accessible to interested
individuals/parties. Furthermore, it would remove the concerns of
creating replacement platforms as each part, or the entire system,
could be replaced relatively inexpensively. Second, the utilization of
a more cost-efficient platform would allow for a better understanding
of the performance requirements necessary for efficiently operating
autonomous vehicles. Finally, we strive to achieve the ability to
compare the real-time performance of multiple embedded computing
platforms.

We display the efficacy of the Picar by training and testing the
DeepTesla DNN \cite{} in a custom-made environment. We find that the
Picar is capable of consistently accomplishing all real-time
operations required for autonomous driving in a 50 millisecond frame.

The remaining sections of the paper are as follows: Section II gives
an overview of the platform, including the high-level system and the
methods used for training and inference. Section III discusses the
ways/methodologies in which training data was collected. Section IV
outlines the network architecture. This is followed by the real-time
DNN inferencing in Section V. Section VI reviews the online/offline
training done with the platform, with an evaluation given in Section
VII. Section VIII gives a discussion of related works, and the paper
finishes with conclusions in Section IX.

\section{Background}
Cite a paper \cite{barroso2009datacenter}.

Cite multiple papers \cite{banga99resourcecontainers,barroso2009datacenter}

\section{Platform Overview}
...
\section{Data Collection}
...
\section{Network Architecture}
...
\section{Real-Time DNN Inferencing}
...
\section{Online/Offline Training}
...
\section{Evaluation}
...
\section{Related Work}
...
\section{Conclusion}
%-------------------------------------------------------------------------

>>>>

\input{intro}
\input{background}

\section{Platform Overview}
...
\section{Data Collection}
...
\section{Network Architecture}
...
\section{Real-Time DNN Inferencing}
...
\section{Online/Offline Training}
...
\section{Evaluation}
...
\section{Related Work}
\cite{Bojarski2016}

\section{Conclusion}
%-------------------------------------------------------------------------
